\documentclass{article}
\usepackage{titlesec}
\usepackage{changepage}
\usepackage{amsmath}
\usepackage[margin=1in]{geometry}

\titleformat*{\subsection}{\bfseries}


\begin{document}
	\section*{Team}
		\begin{itemize}
			\item Team Name: Raspberry Pie
			\item Team Number: 6 
		\end{itemize}
		\subsection*{Team Members:}
		\begin{itemize}
			\item Oliver He
			\item Aaron Mankel
			\item Nik Suyko
			\item Junzhen Wang
			\item Kieran Zylstra
		\end{itemize}
	\section*{Application}
	\textbf{Application Name:} Inspirational Weather
	\subsection*{Application Description:}
	The application will consist of a weather mining web application
	that makes predictions about what the next day of weather. It will use an
	API that gives data in either an xml or json format. It will store this data
	in an SQL database for later retrieval. When a person asks for the weather it
	will get the most current data from the api service and then update the table.
	\par
	The stored data will be used to make a prediction about tommorows
	weather and in order to display past data. Displaying old data is key because
	not many APIs offer this as a service and very few web pages or apps display
	this data. Along with displaying past data and giving a prediction for the next
	day we will display an inspiration quote that is retrieved from another table
	where we will have stored many quotes for circulation
	\section*{Vision Statement}
	The web application is for everyday people who have a need
	of accurate weather data. Inspirational Weather is in a category of a predictive
	web application that gives people past weather data as well as current weather
	and inspirational quotes that unlike other weather apps, gives past weather data.
	\section*{Version Control: Github}
	\begin{itemize}
		\item k2zylstra/SoftwareDev\_ProjectCode
		\item k2zylstra/SoftwareDev\_MeetingLogs
		\item k2zylstra/SoftwareDev\_MilestoneSubmissions
	\end{itemize}
	\section*{Development Method:}
	We will be using agile. Here we defined the scope, and once every two weeks we will
	begin working on a new feature and we should have it finished by the next agile meeting
	Over the two weeks will also be meeting every week and can monitor the launch of our
	feature.
	\section*{Communication Plan:}
	We will keep in touch with discord to make sure everything
	is going according to schedule. Google docs will be used for collaboration on small
	files and Github will be used for meeting logs code and milestone submissions
	\section*{Proposed Architechture Plan:}
	\subsection*{Web Application}
	\begin{itemize}
		\item \textbf{Frontend:} Javascript/React
		\item \textbf{MiddleLayer:} Node.js
		\item \textbf{Backend:} MYSQL
	\end{itemize}
	\section*{Meeting Plan}
	We will be meeting every Tuesday at the Pekoe caffee from 9am to 11am in person.

\end{document}